Inference for multivariate peaks over threshold models

### 2021-12-12 methodology_projgamma.tex
sdf

  Our strategy consists of describing the angular distribution $\Phi$ using a sample based approach with the following steps: (i) Apply the transformation in Equation (\ref{eqn:standardization}) to the original data; (ii) Obtain the subsample of the standardized observations that satisfy $R>1$; (iii) Take a finite $p$ and project the observations onto ${\mathbb S}_p^{d-1}$; (iv) Fit the model in Equation (\ref{eqn:PGmix}) to the resulting data and obtain samples from the fitted model; (v) Project the resulting samples onto ${\mathbb S}_\infty^{d-1}$.
  For step (iv) we use a Bayesian approach that is implemented using a purposely developed Markov chain Monte Carlo that is described in the next section. 
  {\bf Instead of the old Figure 1, it would be nice to add a figure where you illustrate this procedure. Give it a try.}

@@

\subsubsection{Inference for the projected Gamma mixture model}
The Dirichlet process mixture model groups observations into stochastically assigned \emph{clusters}.  Building out the methods of inference for Equation~\ref{eqn:dppg}, let $n_j^{-i}$ be the number of observations in cluster $j$ not including observation $i$.  Let $J^{-i}$ be the number of extant 
% {\bf (remaining?)} observations
clusters, not including any singleton that observation $i$ is in. Under this model, the probability of cluster membership for a given observation is proportional to
\begin{equation*}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\hspace{0.5cm} &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \eta\int\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)dG_0(\bm{\alpha}_j,\bm{\beta}_j)\hspace{0.5cm} &\text{~for~}j = J^{-i} + 1.
        \end{cases}
\end{equation*}
If $G_0$ is not a conjugate prior for the kernel, the integral in the above formula can not be obtained in closed form. Using Algorithm 8 from \cite{neal2000}, we draw $m$ candidate clusters, $\bm{\alpha}_j,\bm{\beta}_j$ for $j = J^{-i} + 1,\ldots, J^{-i} + m$ from $G_0$. Then, we sample the cluster indicator $\delta_i$ from extant or candidate clusters, where the probability of cluster membership is proportional to
\begin{equation}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\hspace{0.5cm} &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \frac{\eta}{m}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\hspace{0.5cm} &\text{~for~}j \in \lbrace J^{-i} + 1,\ldots, J^{-i} + m\rbrace.
        \end{cases}
\end{equation}
If a candidate cluster is selected,
%{\bf you first have to say that you sample from this distribution. What is the ``candidate cluster''?}
then $\delta_i = J = J^{- i} + 1$, and the associated cluster parameters are saved.

>>>>

  Our strategy consists of describing the angular distribution $\Phi$ using a sample based approach with the following steps: (i) Apply the transformation in Equation (\ref{eqn:standardization}) to the original data; (ii) Obtain the subsample of the standardized observations that satisfy $R>1$; (iii) Take a finite $p$ and project the observations onto ${\mathbb S}_p^{d-1}$; (iv) Fit the model in Equation (\ref{eqn:PGmix}) to the resulting data and obtain samples from the fitted model; (v) Project the resulting samples onto ${\mathbb S}_\infty^{d-1}$.
  For step (iv) we use a Bayesian approach that is implemented using a purposely developed Markov chain Monte Carlo that is described in the next section.

@@

\subsubsection{Inference for the projected Gamma mixture model}
The Dirichlet process mixture model groups observations into stochastically assigned \emph{clusters}.  Building out the methods of inference for Equation~\ref{eqn:dppg}, let $n_j^{-i}$ be the number of observations in cluster $j$ not including observation $i$.  Let $J^{-i}$ be the number of extant 
% {\bf (remaining?)} observations
clusters, not including any singleton that observation $i$ is in. Under this model, the probability of cluster membership for a given observation is proportional to
\begin{equation*}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\hspace{0.5cm} &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \eta\int\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)dG_0(\bm{\alpha}_j,\bm{\beta}_j)\hspace{0.5cm} &\text{~for~}j = J^{-i} + 1.
        \end{cases}
\end{equation*}
If $G_0$ is not a conjugate prior for the kernel, the integral in the above formula may not be
available in closed form. Using Algorithm 8 from \cite{neal2000}, by Monte Carlo integration, drawing  $m$ candidate
clusters, $\bm{\alpha}_j,\bm{\beta}_j$ for $j = J^{-i} + 1,\ldots, J^{-i} + m$ from $G_0$. 
Then, we sample the cluster indicator $\delta_i$ from extant or candidate clusters, where
the probability of cluster membership is proportional to
\begin{equation}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\hspace{0.5cm} &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \frac{\eta}{m}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\hspace{0.5cm} &\text{~for~}j \in \lbrace J^{-i} + 1,\ldots, J^{-i} + m\rbrace.
        \end{cases}
\end{equation}
If a candidate cluster is selected,
%{\bf you first have to say that you sample from this distribution. What is the ``candidate cluster''?}
then $\delta_i = J = J^{- i} + 1$, and the associated cluster parameters are saved.

### 2021-12-12 results.tex
sdf

\begin{figure}[htb]
    \centering
    \caption{Pairwise conditional survival curves for selected locations, conditioning on all other dimensions at greater than 90th percentile (fitted)\label{fig:condsurv2d} {\bf The numbers in the plots do not correspond to the number in the text}}
    \includegraphics[height=5in, width=5in]{./images/condsurv_2d}
\end{figure}

>>>>

\begin{figure}[htb]
    \centering
    \caption{Pairwise conditional survival curves for selected locations, conditioning on all other dimensions at greater than 90th percentile (fitted)\label{fig:condsurv2d}}
    \includegraphics[height=5in, width=5in]{./images/condsurv_2d}
\end{figure}
